Gamification Effectiveness on Education

### 2024-04-08 paper/paper.qmd
rough notes about the outline of the paper

>>>>

In this paper, we are doing replication of a study ... , which has a control and treatment where the treatment is applied gamification, while the control is using an ordinary education system. Yeah there benefits, but there are downside when comes to how the gamification as it might discourage learning. Furthermore, an wide use application of gamification is a language learning app called Duolingo, which has ... active users and this app learning is recognized in certain Universities as legitimate English learning.So we examine game design that are use. Ways to apply gamification in daily lives, like this app called Habitica: Gamify your tasks.
